### 2022-01-31 src/text/0-authors.tex

%Opt in solution for the contributor list...

\author{
	Christoph Deil\inst{\ref{inst:mpik}} \and Axel Donath\inst{\ref{inst:mpik}}
	\and Régis Terrier\inst{\ref{inst:apc}} \and Johannes
	King\inst{\ref{inst:mpik}} \and Léa Jouvin\inst{\ref{inst:apc}} \and Manuel Paz
	Arribas\inst{\ref{inst:humboldt}} \and Ellis Owen\inst{\ref{inst:ucl}} \and
	Julien Lefaucheur\inst{\ref{inst:obsparis}} \and Olga
	Vorokh\inst{\ref{inst:olga}} \and Jonathan Harris\inst{\ref{inst:jon}} \and
	Brigitta Sipocz\inst{\ref{inst:brigitta1}, \ref{inst:brigitta2}} \and Dirk
	Lennarz\inst{\ref{inst:atlanta}} \and Helen Poon\inst{\ref{inst:mpik}} \and
	Nachiketa Chakraborty\inst{\ref{inst:mpik}} \and Domenico
	Tiziani\inst{\ref{inst:erlangen}} \and Luigi Tibaldo\inst{\ref{inst:mpik}} \and
	Victor Zabalza\inst{\ref{inst:victor}} \and Rolf Bühler\inst{\ref{inst:desy}}
	\and Stefan Klepser\inst{\ref{inst:desy}} \and Ignasi
	Reichardt\inst{\ref{inst:padova}} }

\institute{
Max-Planck-Institut f\"{u}r Kernphysik, Heidelberg, Germany \label{inst:mpik}
\and APC, University of Paris 7, France \label{inst:apc} \and LUTH,
Observatoire de Paris, Meudon, France \label{inst:obsparis} \and DESY, Zeuthen,
Germany \label{inst:desy} \and Humboldt University, Berlin, Germany
\label{inst:humboldt} \and UCL-MSSL, Dorking, United Kingdom \label{inst:ucl}
\and INFN, Padova, Italy \label{inst:padova} \and Belarusian State University,
Belarus, Minsk \label{inst:olga} \and FAU, Erlangen, Germany
\label{inst:erlangen} \and School of Physics and Center for Relativistic
Astrophysics, Georgia Institute of Technology, Atlanta, GA, USA
\label{inst:atlanta} \and Centre for Astrophysics Research, University of
Hertfordshire, College Lane, Hatfield, AL10 9AB, UK \label{inst:brigitta1} \and
Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge, CB3
0HA, UK \label{inst:brigitta2} \and Department of Physics, Durham University,
South Road, Durham, DH1 3LE, UK \label{inst:jon} \and TODO: Victor address
\label{inst:victor} }

>>>>

\author{
	Axel Donath \inst{\ref{inst:6}} \and
	Christoph Deil \inst{\ref{inst:13}} \and
	Régis Terrier \inst{\ref{inst:2}} \and
	Johannes King \inst{\ref{inst:22}} \and
	Jose Enrique Ruiz \inst{\ref{inst:17}} \and
	Quentin Remy \inst{\ref{inst:18}} \and
	Léa Jouvin \inst{\ref{inst:unknown}} \and
	Atreyee Sinha \inst{\ref{inst:26}} \and
	Matthew Wood \inst{\ref{inst:11}} \and
	Fabio Pintore \inst{\ref{inst:14}} \and
	Manuel Paz Arribas \inst{\ref{inst:unknown}} \and
	Laura Olivera \inst{\ref{inst:18}} \and
	Luca Giunti \inst{\ref{inst:2}} \and
	Bruno Khelifi \inst{\ref{inst:3}} \and
	Ellis Owen \inst{\ref{inst:21}} \and
	Brigitta Sipőcz \inst{\ref{inst:5}} \and
	Olga Vorokh \inst{\ref{inst:unknown}} \and
	Julien Lefaucheur \inst{\ref{inst:unknown}} \and
	Fabio Acero \inst{\ref{inst:7}} \and
	Thomas Robitaille \inst{\ref{inst:1}} \and
	David Fidalgo \inst{\ref{inst:unknown}} \and
	Jonathan D. Harris \inst{\ref{inst:unknown}} \and
	Cosimo Nigro \inst{\ref{inst:15}} \and
	Lars Mohrmann \inst{\ref{inst:18}} \and
	Dirk Lennarz \inst{\ref{inst:0}} \and
	Jalel Eddine Hajlaoui \inst{\ref{inst:2}} \and
	Alexis de Almeida Coutinho \inst{\ref{inst:27}} \and
	Matthias Wegenmat \inst{\ref{inst:unknown}} \and
	Dimitri Papadopoulos \inst{\ref{inst:unknown}} \and
	Maximilian Nöthe \inst{\ref{inst:25}} \and
	Nachiketa Chakraborty \inst{\ref{inst:unknown}} \and
	Michael Droettboom \inst{\ref{inst:20}} \and
	Helen Poon \inst{\ref{inst:unknown}} \and
	Arjun Voruganti \inst{\ref{inst:unknown}} \and
	Jason Watson \inst{\ref{inst:8}} \and
	Thomas Armstrong \inst{\ref{inst:unknown}} \and
	Vikas Joshi \inst{\ref{inst:12}} \and
	Erik Tollerud \inst{\ref{inst:24}} \and
	Erik M. Bray \inst{\ref{inst:unknown}} \and
	Domenico Tiziani \inst{\ref{inst:unknown}} \and
	Gabriel Emery \inst{\ref{inst:unknown}} \and
	Hubert Siejkowski \inst{\ref{inst:unknown}} \and
	Kai Brügge \inst{\ref{inst:23}} \and
	Luigi Tibaldo \inst{\ref{inst:16}} \and
	Arpit Gogia \inst{\ref{inst:unknown}} \and
	Ignacio Minaya \inst{\ref{inst:unknown}} \and
	Marion Spir-Jacob \inst{\ref{inst:unknown}} \and
	Yves Gallant \inst{\ref{inst:unknown}} \and
	Andrew W. Chen \inst{\ref{inst:9}} \and
	Roberta Zanin \inst{\ref{inst:4}} \and
	Jean-Philippe Lenain \inst{\ref{inst:unknown}} \and
	Larry Bradley \inst{\ref{inst:24}} \and
	Kaori Nakashima \inst{\ref{inst:12}} \and
	Anne Lemière \inst{\ref{inst:2}} \and
	Mathieu de Bony \inst{\ref{inst:unknown}} \and
	Matthew Craig \inst{\ref{inst:unknown}} \and
	Lab Saha \inst{\ref{inst:6}} \and
	Zé Vinicius \inst{\ref{inst:unknown}} \and
	Kyle Barbary \inst{\ref{inst:unknown}} \and
	Thomas Vuillaume \inst{\ref{inst:28}} \and
	Adam Ginsburg \inst{\ref{inst:unknown}} \and
	Daniel Morcuende \inst{\ref{inst:unknown}} \and
	José Luis Contreras \inst{\ref{inst:unknown}} \and
	Laura Vega Garcia \inst{\ref{inst:unknown}} \and
	Oscar Blanch Bigas \inst{\ref{inst:unknown}} \and
	Víctor Zabalza \inst{\ref{inst:unknown}} \and
	Wolfgang Kerzendorf \inst{\ref{inst:19}} \and
	Rolf Buehler \inst{\ref{inst:10}} \and
	Sebastian Panny \inst{\ref{inst:unknown}} \and
	Silvia Manconi \inst{\ref{inst:unknown}} \and
	Stefan Klepser \inst{\ref{inst:10}} \and
	Peter Deiml \inst{\ref{inst:unknown}} \and
	Johannes Buchner \inst{\ref{inst:unknown}} \and
	Hugo van Kemenade \inst{\ref{inst:unknown}} \and
	Eric O. Lebigot \inst{\ref{inst:unknown}} \and
	Benjamin Alan Weaver \inst{\ref{inst:unknown}} \and
	Debanjan Bose \inst{\ref{inst:unknown}} \and
	Rubén López-Coto \inst{\ref{inst:unknown}} \and
	Sam Carter \inst{\ref{inst:unknown}}
}

\institute{
	Amazon, Atlanta GA, US \label{inst:0} \and
	Aperio Software, Insight House, Riverside Business Park, Stoney Common Road, Stansted, Essex, CM24 8PL, UK \label{inst:1} \and
	Astroparticle and Cosmology Laboratory CNRS, Université de Paris, 10 Rue Alice Domon et Léonie Duquet, 75013 Paris, France \label{inst:2} \and
	CNRS \label{inst:3} \and
	CTA Observatory gGmbH, Via Piero Gobetti 93/3 40129 Bologna, Italy \label{inst:4} \and
	California Institute of Technology, Pasadena CA, US \label{inst:5} \and
	Center for Astrophysics | Harvard \& Smithsonian, CfA, 60 Garden St., 02138 Cambridge MA, US \label{inst:6} \and
	DAp/AIM, CEA-Saclay/CNRS, France \label{inst:7} \and
	DESY \label{inst:8} \and
	Department of Physics, University of the Free State, PO Box339, Bloemfontein 9300, South Africa \label{inst:9} \and
	Deutsches Elektronen-Synchrotron, DESY, Platanenallee 6 15738 Zeuthen, Germany \label{inst:10} \and
	Facebook, 1 Hacker Way, Menlo Park, CA 94025, US \label{inst:11} \and
	Friedrich-Alexander-Universität Erlangen-Nürnberg, Erlangen Centre for Astroparticle Physics, Erwin-Rommel-Str. 1 91058 Erlangen, Germany \label{inst:12} \and
	HeidelbergCement AG, Berliner Straße 6, 69120 Heidelberg, Germany \label{inst:13} \and
	INAF/IASF, via Ugo La Malfa 153,  90146 Palermo, Italy \label{inst:14} \and
	Institut de Fisica d'altes Energies, IFAE, Edifici Cn, Campus UAB, 08193 Bellaterra (Barcelona), Spain \label{inst:15} \and
	Institute de Recherche en Astrophysique et Planetologie, IRAP, \label{inst:16} \and
	Instituto de Astrofísica de Andalucía - CSIC, Gta. de la Astronomía, 18008 Granada, Spain \label{inst:17} \and
	Max Planck Institut für Kernphysik, MPIK, Saupfercheckweg 1, 69117 Heidelberg, Germany \label{inst:18} \and
	Michigan State University, Department of Physics and Astronomy, 428 S Shaw Ln East Lansing, MI 48824, US \label{inst:19} \and
	Mozilla, Mountain View, CA \label{inst:20} \and
	National Tsing Hua University Institute of Astronomy, Hsinchu, Taiwan \label{inst:21} \and
	Pamyra \label{inst:22} \and
	Point 8 GmbH, Rheinlanddamm 201, 44139 Dortmund, Germany \label{inst:23} \and
	Space Telescope Science Institute, STScI, 3700 San Martin Drive, 21218 Baltimore MD, US \label{inst:24} \and
	TU Dortmund University, Otto-Hahn-Str. 4a 44227 Dortmund, Germany \label{inst:25} \and
	Universidad Complutense de Madrid EMFTEL, UCM, Plaza de la Ciencias, 28040 Madrid, Spain \label{inst:26} \and
	Universidade de São Paulo, Brazil \label{inst:27} \and
	Université Savoie Mont Blanc, CNRS, Laboratoire d’Annecyde Physique des Particules - IN2P3, 74000 Annecy, France \label{inst:28} \and
	unknown \label{inst:unknown}
}
